A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-30 sections/Discussion.tex
typo

\subsection{Lexically-scoped type variables}
We fhave urther extended the type system with support for
lexically-scoped type variables~\cite{scoped-type-variables}.
Our Abella formalization for this extension proves
all the metatheory we discuss here.

>>>>

\subsection{Lexically-scoped type variables}
We have further extended the type system with support for
lexically-scoped type variables~\cite{scoped-type-variables}.
Our Abella formalization for this extension proves
all the metatheory we discuss in Section~\ref{sec:metatheory}.
